\begin{acknowledgements}
I would like to express my deepest appreciation to many individuals and organisations who have supported me to complete my project. A special gratitude to my project supervisor, Prof. Daniel Kroening and his research assistant, Martin Brain. I am grateful for their friendly advice and encouragements, especially for numerous consultations and their enlightening views on the structural improvement of my report. I am also thankful to Ernie Cohen, Principal Software Engineer at Amazon Web Services and Dr Michael Tautsching, Lecturer at the Queen Mary University of London, who have explained me the structure of s2n and clarified some basic issues on the CBMC operations, respectively, at the early stage of my project.

Moreover, I would like to thank my program supervisor, Prof. Michael Benedikt, who have warmly guided me in academics during the year.

I appreciate my sponsors, Alistar Harvey Foundation Scholarship, who have fully sponsored my study at the University of Oxford. Thanks for their generosity, I could complete my master's study without worrying about my financial status. 

A special thanks to Keith Leung, Jason Mo, Jacky Chan and Brenda Sham for proof-reading my dissertation and saving it from a mess of poor English.

Last but not least, I would like to express my deepest gratitude to my parents and Brenda Sham, my girlfriend, for their moral supports and maintaining the quality of my life on daily basis. Their supports and encouragements have made the complete of my dissertation possible and have allowed me to realise my potential.
\end{acknowledgements}